A Constructive Metatheory of Bidirectional Type Synthesis for Simple Types

### 2023-06-13 tex/sec5-synthesis.tex
[ tex ] Update notation

  \begin{description}
    \item[(var)] If $x : A$ is in the context $\Gamma$, then there exists a type $A$ such that $\Gamma \vdash_{\Sigma, \Omega} x \Rightarrow A$.
      Otherwise, if $\Gamma \vdash_{\Sigma, \Omega} x \Rightarrow A$ is derivable, then by inversion $(x : A)$ must be in $\Gamma$, a contradiction.
    \item[(anno)]
    \item[(sub)]
%    \item For every mode-correct operation $o \colon \Xi \rhd [\Delta_1]A_{1}^{d_1}, \ldots, [\Delta_{n}] A^{d_n}_{n} \to A^{d}$, a context $\Gamma$, and a raw term
%      \[
%        \isTerm{\tmOp_{o}(\vec{x}_1.t_1,\ldots, \vec{x}_n.t_n)}, 
%      \]
%      with a mode $d$, it is decidable that there exists a substitution $\rho$ from $\Xi$ to $\emptyset$ and a typing derivation of
%      \[
%        \Gamma \vdash_{\Sigma, \Omega} \isTerm{\tmOp_{o}(\vec{x}_1.t_1,\ldots, \vec{x}_n.t_n)} : \simsub{A}{\rho}^\isDir{d}.
%      \]
    \item For every set $\Xi$ of type variables, list of
      \[
        \left(\Delta_i, A_i, d_i\right) : \Cxt_{\Sigma}(\Xi) \times \Type_{\Sigma}(\Xi) \times \Mode, 
      \]
      \emph{partial} substitution $\rho$ from $\Xi$ to $\emptyset$, context $\Gamma$, and raw terms $t_i$'s in mode $d_i$,
      \begin{enumerate}
        \item either there is a minimal extension $\ext{\rho}$ of $\rho$ such that all     of following judgements are derivable
          \[
            \Gamma, \simsub{\Delta_i}{\ext{\rho}} \vdash_{\Sigma, \Omega} t_i \colon \simsub{A_i}{\ext{\rho}}^{d_i}
          \]

        \item or there is no extension $\ext{\rho}$ such that all $\Gamma, \simsub{\Delta_i}{\ext{\rho}} \vdash_{\Sigma, \Omega} t_i \colon \simsub{A_i}{\ext{\rho}}^{d_i}$ has a typing derivation. 
      \end{enumerate}
  \end{description}
\end{proof}

>>>>

  \begin{description}
    \item[(var)] If $x : A$ is in the context $\Gamma$, then there exists a type $A$ such that $\Gamma \vdash_{\Sigma, \Omega} x \Rightarrow A$.
      Otherwise, if $\Gamma \vdash_{\Sigma, \Omega} x \Rightarrow A$ is derivable, then by inversion $(x : A)$ must be in $\Gamma$, a contradiction.
    \item[(anno)]
    \item[(sub)]
%    \item For every mode-correct operation $o \colon \Xi \rhd [\Delta_1]A_{1}^{d_1}, \ldots, [\Delta_{n}] A^{d_n}_{n} \to A^{d}$, a context $\Gamma$, and a raw term
%      \[
%        \isTerm{\tmOp_{o}(\vec{x}_1.t_1,\ldots, \vec{x}_n.t_n)}, 
%      \]
%      with a mode $d$, it is decidable that there exists a substitution $\rho$ from $\Xi$ to $\emptyset$ and a typing derivation of
%      \[
%        \Gamma \vdash_{\Sigma, \Omega} \isTerm{\tmOp_{o}(\vec{x}_1.t_1,\ldots, \vec{x}_n.t_n)} : \simsub{A}{\rho}^\isDir{d}.
%      \]
    \item For every set $\Xi$ of type variables, list of
      \[
        \left(\Delta_i, A_i, d_i\right) : \Cxt_{\Sigma}(\Xi) \times \Type_{\Sigma}(\Xi) \times \Mode, 
      \]
      for $i = 1, \ldots, n$, \emph{partial} substitution $\rho$ from $\Xi$ to $\emptyset$, context $\Gamma$, and raw terms $t_i$'s in mode $d_i$,
      \begin{enumerate}
        \item either there is a minimal extension $\ext{\rho}$ of $\rho$ such that all     of following judgements are derivable
          \[
            \Gamma, \simsub{\Delta_i}{\ext{\rho}} \vdash_{\Sigma, \Omega} t_i \colon \simsub{A_i}{\ext{\rho}}^{d_i}
          \]

        \item or there is no extension $\sigma$ such that all $\Gamma, \simsub{\Delta_i}{\sigma} \vdash_{\Sigma, \Omega} t_i \colon \simsub{A_i}{\sigma}^{d_i}$ has a typing derivation. 
      \end{enumerate}
  \end{description}
\end{proof}
